---
title: "PHA Exit Demographics"
author: "Public Health - Seattle & King County"
date: "9/2/2021"
output: html_document
---

```{=html}
<style type="text/css">

h1 { color: DarkBlue;}
h2 { color: DarkBlue;}
h3 { color: DarkBlue;}
h4 { color: DarkBlue;}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  fig.width = 9,
  fig.asp = 0.8,
  out.width = "100%"
  )
options(knitr.table.format = "html") 
```

<span style="color: red;">**Data are preliminary and not for distribution.**</span>

The data below show demographics of people who exited from King County Housing Authority or Seattle Housing Authority between 2012 and 2020. Note the following limitations:

-   KCHA data is incomplete for exits prior to late 2015.
-   Only complete exits are included here. People with action type = 6 who had subsequent 50058 records are not considered to have exited.
-   Exit types are categorized according to the document here: <https://github.com/PHSKC-APDE/hud_hears/blob/main/data_processing/PHA_exit_definitions.csv>.

# Individual-level analyses
## Exits over time
### Proportion of people exiting
-   Approximately 5% of KCHA and SHA residents exit in a given year, excluding 2020 when the COVID pandemic reduced this proportion.
```{r exitprop, fig.asp=0.7, fig.width=10}
any_exit %>%
  ggplot(aes(fill = as.character(exited), y = n_supp, x = exit_year)) +
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2.5, show.legend = F,
            aes(group = exited, label = paste0(pct_supp, "%"),
                color = exited)) +
  scale_color_manual(values = c("white", "black")) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 3) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Proportion of people exiting by year",
       x = "Year",
       y = "Percent of people",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit vs. not") +
  facet_grid(~ agency)
```


### Type of exits by year

-   Both positive and negative exits increased over time at SHA before a sharp decrease in 2020.
-   There was no clear pattern of KCHA exits between 2016 (the first year full exit data were available) and 2020 beyond a decline in negative exits.
-   Numbers of positive and negative exits from SHA were largely the same across 2012 to 2019, before a decline in 2020.

```{r year}
# Line graph showing numbers over time
ggplot(exit_year, aes(group = exit_category, y = n_supp, x = exit_year, color = exit_category)) + 
  geom_line(size = 1) +
  scale_color_viridis(discrete = T) +
  theme_ipsum() + 
  labs(title = "Number of exits from KCHA and SHA",
       x = "Year",
       y = "Number of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.") +
  facet_wrap(~agency)
```


-   The proportion of KCHA exits due to positive reasons increased over time, peaking at `r kcha_max_pos$pct`% in `r glue_collapse(unique(kcha_max_pos$exit_year), sep = ", ", last = ", and ")`.
-   Negative exits decreased as a proportion of all KCHA exits from 2016 to 2020.
-   The proportion of SHA exits for positive reasons was flat between 2012 and 2017, but increased to `r sha_max_pos$pct`% in `r glue_collapse(unique(sha_max_pos$exit_year), sep = ", ", last = ", and ")`.
-   The proportion of all SHA exits that were negative was largely unchanged over time.

```{r exitstackyear}
# Stacked percent bar graph
ggplot(exit_year, aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2.5, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 3) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(grid = F) +
  labs(title = "Exit types by year",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_wrap(~agency)
```

## Exits by demographics
### Exits by age
```{r age-stack, fig.asp=1.3}
# Stacked percent bar graph for age group
exit_demogs_sum %>%
  filter(category == "agegrp_expanded" & !is.na(group) & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Exit types by year and age group",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by gender
```{r gender-stack}
exit_demogs_sum %>%
  filter(category == "gender_recent" & !is.na(group) & group != "Unknown" & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Exit types by year and gender",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by race/ethnicity
```{r race-stack, fig.asp=1.2}
# Stacked percent bar graph for age group
exit_demogs_sum %>%
  filter(category == "race_eth_me" & !is.na(group) & group != "Unknown" & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Exit types by year and race/ethnicity",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by time in housing
```{r los-stack}
# Stacked percent bar graph for age group
exit_demogs_sum %>%
  filter(category == "time_housing" & !is.na(group) & group != "Unknown" & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Exit types by year and length of time in housing",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by program type
```{r prog-stack}
# Stacked percent bar graph for age group
exit_demogs_sum %>%
  filter(category == "major_prog" & !is.na(group) & group != "Unknown" & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Exit types by year and program type",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by portfolio
```{r portfolio-kcha-stack}
exit_demogs_sum %>%
  filter(agency == "KCHA") %>%
  filter(category == "portfolio_final" & !is.na(group) & group != "Unknown" & exit == 1) %>%
  ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 1.5) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Exit types by year and portfolio (KCHA)",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_wrap(~ group, ncol = 3)
```

```{r portfolio-sha-stack}
exit_demogs_sum %>%
  filter(agency == "SHA") %>%
  filter(category == "portfolio_final" & !is.na(group) & group != "Unknown" & exit == 1) %>%
  ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Exit types by year and portfolio (SHA)",
       x = "Year",
       y = "Percent of exits",
       caption = "NB.",
       fill = "Exit category") +
  facet_wrap(~ group)
```


# Household-level analyses
## Exits over time
### Proportion of people exiting
-   Approximately 6-7% of KCHA and SHA households exit in a given year, excluding 2020 when the COVID pandemic reduced this proportion (to <1% for SHA).
```{r exitprop-hh, fig.asp=0.7, fig.width=10}
any_exit_hh %>%
  ggplot(aes(fill = as.character(exited), y = n_supp, x = exit_year)) +
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2.5, show.legend = F,
            aes(group = exited, label = paste0(pct_supp, "%"),
                color = exited)) +
  scale_color_manual(values = c("white", "black")) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 3) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Proportion of households exiting by year",
       x = "Year",
       y = "Percent of households",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit vs. not") +
  facet_grid(~ agency)
```


### Type of exits by year

-   Both positive and negative exits increased over time at SHA before a sharp decrease in 2020.
-   There was no clear pattern of KCHA exits between 2016 (the first year full exit data were available) and 2020. Though there was a decrease in exits in 2020, it was not as substantial as for SHA.

```{r year-hh}
# Line graph showing numbers over time
ggplot(exit_year_hh, aes(group = exit_category, y = n_supp, x = exit_year, color = exit_category)) + 
  geom_line(size = 1) +
  scale_color_viridis(discrete = T) +
  theme_ipsum() + 
  labs(title = "Number of household exits from KCHA and SHA",
       x = "Year",
       y = "Number of household exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.") +
  facet_wrap(~agency)
```


-   The proportion of households exiting KCHA due to positive reasons increased over time, peaking at `r kcha_max_pos_hh$pct`% in `r glue_collapse(unique(kcha_max_pos_hh$exit_year), sep = ", ", last = ", and ")`.
-   Negative exits decreased as a proportion of all KCHA household exits from 2016 to 2020.
-   The proportion of household exits at SHA for positive reasons was flat between 2012 and 2017, but increased in the following years to `r sha_max_pos_hh$pct`% in `r glue_collapse(unique(sha_max_pos_hh$exit_year), sep = ", ", last = ", and ")`.
-   Negative exits increased as a proportion of all SHA household exits over time.

```{r stackyear-hh}
# Stacked percent bar graph
ggplot(exit_year_hh, aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2.5, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 3) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(grid = F) +
  labs(title = "Household exit types by year",
       x = "Year",
       y = "Percent of household exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_wrap(~agency)
```

## Exits by demographics
NB. Demographics categories are based on the head of household

### Exits by age
```{r age-stack-hh, fig.asp=1.3}
# Stacked percent bar graph for age group
exit_demogs_sum_hh %>%
  filter(category == "agegrp_expanded" & !is.na(group) & !group %in% c("<10", "10-17") & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Household exit types by year and age group",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by gender
```{r gender-stack-hh}
exit_demogs_sum_hh %>%
  filter(category == "gender_recent" & !is.na(group) & group != "Unknown" & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Household exit types by year and gender",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by race/ethnicity
```{r race-stack-hh, fig.asp=1.2}
# Stacked percent bar graph for age group
exit_demogs_sum_hh %>%
  filter(category == "race_eth_me" & !is.na(group) & group != "Unknown" & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Household exit types by year and race/ethnicity",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by time in housing
```{r los-stack-hh}
# Stacked percent bar graph for age group
exit_demogs_sum_hh %>%
  filter(category == "time_housing" & !is.na(group) & group != "Unknown" & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Household exit types by year and length of time in housing",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by program type
```{r prog-stack-hh}
# Stacked percent bar graph for age group
exit_demogs_sum_hh %>%
  filter(category == "major_prog" & !is.na(group) & group != "Unknown" & exit == 1) %>%
ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Household exit types by year and program type",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_grid(group ~ agency)
```

### Exits by portfolio
```{r portfolio-kcha-stack-hh}
exit_demogs_sum_hh %>%
  filter(agency == "KCHA") %>%
  filter(category == "portfolio_final" & !is.na(group) & group != "Unknown" & exit == 1) %>%
  ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Household exit types by year and portfolio (KCHA)",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015",
       fill = "Exit category") +
  facet_wrap(~ group)
```

```{r portfolio-sha-stack-hh}
exit_demogs_sum_hh %>%
  filter(agency == "SHA") %>%
  filter(category == "portfolio_final" & !is.na(group) & group != "Unknown" & exit == 1) %>%
  ggplot(aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 2) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(axis_text_size = 10, grid = F) +
  labs(title = "Household exit types by year and portfolio (SHA)",
       x = "Year",
       y = "Percent of exits",
       caption = "NB.",
       fill = "Exit category") +
  facet_wrap(~ group)
```

# SENSITIVITY ANALYSES WITH DEATHS REMOVED
## Exits over time
### Type of exits by year


```{r year-nodeath}
# Line graph showing numbers over time
ggplot(exit_year_nodeath, aes(group = exit_category, y = n_supp, x = exit_year, color = exit_category)) + 
  geom_line(size = 1) +
  scale_color_viridis(discrete = T) +
  theme_ipsum() + 
  labs(title = "Number of exits from KCHA and SHA (excluding exits due to deaths)",
       x = "Year",
       y = "Number of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.") +
  facet_wrap(~agency)
```


```{r stackyear-nodeath}
# Stacked percent bar graph
ggplot(exit_year_nodeath, aes(fill = exit_category, y = n_supp, x = exit_year)) + 
  geom_bar(position = "fill", stat="identity", colour = "black") +
  geom_text(position = position_fill(vjust = 0.5), size = 2.5, show.legend = F,
            aes(group = exit_category, label = paste0(pct_supp, "%"),
                color = exit_category)) +
  scale_color_manual(values = label_col) +
  geom_text(aes(x = exit_year, y = 1.02, label = year_tot_label), vjust = 0, size = 3) +
  scale_fill_viridis(discrete = T) +
  scale_y_continuous(labels = scales::percent) +
  theme_ipsum(grid = F) +
  labs(title = "Exit types by year",
       x = "Year",
       y = "Percent of exits",
       caption = "NB. KCHA exit data is incomplete prior to October 2015.",
       fill = "Exit category") +
  facet_wrap(~agency)
```